 Casting multiple shadows: interactive data visualisation with tours and embeddings

### 2020-02-05 paper.Rmd
draft paragraph

@@

## Case Study 2: non-spherical clusters, pdfsense

## Case Study 3: well-clustered data, single cell

## Case Study 4: quickdraw

>>>>

Broadly characterised by @Brehmer2014-hk, characterised two main workflow
steps that an analyst performs when using embedding methods: dimension reduction
and cluster orientation. The first relates to 
dimension reduction achieved by using an embedding method, here an analyst
wants to characterise and map meaning onto the embedded form, for example
identifying batch effects from a high throughput sequencing experiment, or
identifying a gradient along the embedded form. The second relates to using
embeddings as part of a clustering workflow. Here analysts are interested
in identifying  and naming clusters and verifying them by either applying 
known labels or colouring by variables that are a-priori known to distinguish 
clusters.

@@

## Case Study 2: well-clustered smallish single cell

## Case Study 3: largeish single cell data

## Case Study 4: non-spherical clusters, pdfsense
